---
title: "project2"
author: "Anh Nguyen"
date: '`r Sys.Date()`'
output: html_document
---

# Library

```{r}
# analysis
library(tidyverse)
library(car)
library(haven)
# residuals for glmm
library(DHARMa)
# fit glmm
library(lme4)
# fit gee
library(gee)
# graph
library(lattice)
# influenential point
library(influence.ME)
# pretty table
library(sjPlot)
library(gtsummary)
library(labelled)
library(flextable)
library(webshot)
```

# Seed

```{r}
set.seed(3)
```

# Data

```{r}
df <- read_dta('publicrepfile.dta')
```

```{r}
df1 <- df |> 
  dplyr::select('GERMANE', 'prepost', 'VIEWS', 'TTID', 'treatment') |>
  drop_na() |>
  mutate_at(c('GERMANE', 'prepost', 'TTID', 'treatment'), 
            as.factor) |>
  filter(GERMANE != 3)
```

```{r}
var_label(df1) <- list(GERMANE = "Related to mental health theme",
                       prepost = "Pre or post treatment",
                       VIEWS = "Views",
                       TTID = "ID",
                       treatment = "Treatment group")
```



# EDA

## Univariate

```{r}
summary(df1)
```

```{r}
df1 %>% 
  select_if(is.numeric) %>%  
  gather(cols, value) %>%  
  ggplot(aes(x = value)) + 
  geom_boxplot() + 
  facet_grid(.~cols)
```

## Multivariate

```{r}
df1 |>
  filter(GERMANE == 1) |>
  ggplot(aes(y=TTID, x=log(VIEWS+1), colour = prepost)) +
  geom_boxplot(outlier.shape = NA) +
  facet_grid(treatment ~ .) +
  theme(
        axis.text.y=element_blank(),  #remove y axis labels
        axis.ticks.y=element_blank()  #remove y axis ticks
        )

df1 |>
  filter(GERMANE == 2) |>
  ggplot(aes(y=TTID, x=log(VIEWS+1), colour = prepost)) +
  geom_boxplot(outlier.shape = NA) +
  facet_grid(treatment ~ .) +
  theme(
        axis.text.y=element_blank(),  #remove y axis labels
        axis.ticks.y=element_blank()  #remove y axis ticks
        )
```


# Research Question

## Fit

```{r}
m1 <- lmer(log(VIEWS+1) ~ treatment + (1|TTID) + prepost + GERMANE, 
              data=df1)
summary(m1)
```


## Diagnostics

Fixed 

+ Model structure capture the systematic effects
+ normality of residuals
+ variance homogeneity of residuals
+ independence of residuals
+ outliers
+ influenctial observations

Random

+ random effects normality

### Residuals plots

```{r}
simulationOutput <- simulateResiduals(m1, n = 1000)
plot(simulationOutput)
```

```{r}
# calculating aggregated residuals per group
simulationOutputGrp <- recalculateResiduals(simulationOutput, group = df1$TTID)
plot(simulationOutputGrp, quantreg = FALSE)
```

### Across groups

```{r}
plotResiduals(simulationOutput, form = df1$treatment)
plotResiduals(simulationOutput, form = df1$prepost)
#plotResiduals(simulationOutput, form = df1$GERMANE)
```


### Random effect

```{r}
dotplot(ranef(m1,condVar=TRUE),
          lattice.options=list(layout=c(1,2)))
```

```{r}
qqmath(ranef(m1,condVar=TRUE),
          lattice.options=list(layout=c(1,2)))
```

```{r}
r_int <- ranef(m1,condVar=TRUE)$TTID$`(Intercept)`
qqPlot(r_int)
ranef(m1,condVar=TRUE)$TTID |>
  filter(`(Intercept)` %in% r_int[c(14, 54)])
```


### VIF

```{r}
vif(m1)
```


### Outliers

```{r}
m1.infl <- influence(m1, obs = T)
plot(cooks.distance(m1.infl))
```


## Refit

```{r}
# remove group outliers
df2 <- df1 |>
  filter(! TTID %in% c('MH-23', 'MH-92'))
m2 <- lmer(log(VIEWS+1) ~ treatment + (1|TTID) + prepost + GERMANE, 
              data=df2)
summary(m2)
```


```{r}
simulationOutput2 <- simulateResiduals(m2)
plot(simulationOutput2)

# calculating aggregated residuals per group
simulationOutputGrp2 <- recalculateResiduals(simulationOutput2, group = df2$TTID)
plot(simulationOutputGrp2, quantreg = FALSE)

# across groups
plotResiduals(simulationOutput, form = df1$treatment)
plotResiduals(simulationOutput, form = df1$prepost)
plotResiduals(simulationOutput, form = df1$GERMANE)

# random effect
dotplot(ranef(m2,condVar=TRUE),
          lattice.options=list(layout=c(1,2)))
```


# Inference

```{r}
VarCorr(m1)
```


```{r}
drop1(m1,test="Chisq")
```

```{r}
m2<-lmer(VIEWS ~ (1|TTID) + prepost + GERMANE, data=df1)
anova(m2,m1)
```

```{r}
confint(m1)
```

# Output for report

```{r}
df1 |>
  mutate(GERMANE = factor(GERMANE, 
                          levels=c('1','2','3'),
                          labels=c('Related', 'Unrelated','NA')),
         prepost = factor(prepost,
                          levels = c('0', '1', '2'),
                          labels = c('Before', 'During', 'After')),
         treatment = factor(treatment,
                            levels = c('0', '1', '2'),
                            labels = c('Control', 'Digital kit only', 'In person training'))
         )
```


```{r}
df1 |>
  mutate(GERMANE = factor(GERMANE, 
                          levels=c('1','2','3'),
                          labels=c('Related', 'Unrelated','NA')),
         prepost = factor(prepost,
                          levels = c('0', '1', '2'),
                          labels = c('Before', 'During', 'After')),
         treatment = factor(treatment,
                            levels = c('0', '1', '2'),
                            labels = c('Control', 'Digital kit only', 'In person training'))
         ) |>
  select(-TTID) |>
  tbl_summary(
    by = treatment,
    missing_text = "(Missing)",
    statistic = list(all_continuous() ~ "{mean} ± {sd}"),
    label = list(GERMANE ~ "Related to mental health", prepost ~ "Time relative to treatment")
    ) |> 
  add_overall() %>%
  as_flex_table() %>% 
  save_as_image(path = "characteristic_table.png")
```

```{r}
m1 |>
  tbl_regression(
    label = list(
      treatment ~ "Treatment group",
      prepost ~ "Pre or post treatment",
      GERMANE ~ "Related to mental health"
    ), 
    tidy_fun = function(...) broom.mixed::tidy(...)
  ) %>%
  as_flex_table() %>% 
  save_as_image(path = "association_table.png")
```

```{r}
tab_model(m1, file = "model.html")
webshot("model.html", "model.png")
```

# Package version 

```{r}
# export citation 
knitr::write_bib("packages.bib")
```


```{r}
sessionInfo()
```

